Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
brushing up.

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation, we also make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

Automating such as test discovery and continuous integration (CI) ~\cite{ci} 
is an important aspect of BDD. TBD: need to say somting.

@@

\item
    Introduce a set of combinators to set expectations about
    \emph{code examples} for use with Hspec. (Section \ref{sec:for-developers})

@@

\begin{quote}
    TBD: Important points we want to say about BDD:
    \begin{itemize}
        \item
            BDD uses expectations instead of assertions
    \end{itemize}
\end{quote}

@@

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as assertions in xUnit
    testing frameworks, but use a different terminology.

@@

A good candidate for this is Doctest in Python community.
It extends Python's documentation strings so that they
can contain examples.
Examples can be tested by the Python interpreter.

@@

        Hspec does not yet provide a mechanism to set expectations
        about the outcome of code examples.  It uses HUnit assertions
        instead.

@@

We propose several combinators, that can be used to set expectations
about the outcome of code examples.  And we build them on top of
HUnit.

@@

\subsection{Combinators for expectations}

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence}\/s for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for evidences for users.
To specify evidences for developers,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

Automating such as test discovery and continuous integration (CI) ~\cite{ci} 
is an important aspect of BDD.
We improve CI suport for Doctest and Hspec.

@@

\item
    Introduce a set of combinators to set expectations about
    code examples (simply ``code'' hereafter) for use with Hspec. (Section \ref{sec:for-developers})

@@

@@

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertion}\/s in xUnit
    testing frameworks, but use a different terminology.

@@

A good candidate to describe evidences for users is Doctest in Python community.
It extends Python's documentation strings so that they
can contain examples.
Examples can be tested by the Python interpreter.

@@

        Hspec does not yet provide a mechanism to set expectations
        about the outcome of examples.  It uses HUnit assertions
        instead.

@@

We propose several combinators, that can be used to set expectations
about the outcome of examples.  And we build them on top of
HUnit.

@@

\subsection{Hspec combinators for expectations}
